Meta-analysis of fungicide application timing for powdery mildew management

### 2020-02-22 01_Meta-analysis_experiments.Rmd
Line breaks, location formatting, use cache dir

This meta-analysis uses data collected by a number of researchers from the Department of Agriculture and Primary Industries and the University of Southern Queensland. It is worth noting Malcolm Riley and Dr Sue Thompsons effort in establishing and coordinating early field trials between 2010 and 2016.

@@

* 2013  
   + Premer  
   + Millmerran   
   + Mt Mary   
   + Goolhi

@@

```{r Experiment_locations}
experiment_sites <- data.frame(
   location = c(
      "Hermitage Research Station",
      "Red Vale & Kingaroy Research Station",
      "Gatton",
      "Emerald Agricultural College",
      "Bongeen 1 & 2",
      "NGA - Premer",
      "NGA - Millmerran",
      "NGA - Marys Mount",
      "NGA - Goolhi",
      "Missen Flats",
      "Wellcamp"
      ),
   lat = c(-28.215 , -26.58, -27.56, -23.54, -27.51666, -31.43449, -27.923674, -31.0142, -31.00246, -27.905313, -27.564277),
   lon = c(152.1003, 151.83, 152.32, 148.19, 151.450,150.0052, 151.242706, 150.05018, 149.82507, 151.9772,151.867879)
)

write.csv(experiment_sites,"data/Mungbean_experiment_sites.csv", row.names = FALSE)

leaflet(experiment_sites) %>%
   addProviderTiles("Esri.WorldTopoMap") %>%
   setView(lat = -27.31, lng = 150.456,zoom = 5) %>%
   addMarkers(lng = ~lon, lat = ~lat, popup = ~htmlEscape(location))

>>>>

This meta-analysis uses data collected by a number of researchers from the
Department of Agriculture and Primary Industries and the University of Southern
Queensland. It is worth noting Professor Malcolm Riley and Dr Sue Thompson's
effort in establishing and coordinating early field trials between 2010 and
2016.

@@

* 2013  
   + Premer  
   + Millmerran   
   + Marys Mount  
   + Goolhi

@@

```{r Experiment_locations}
experiment_sites <- data.frame(
   location = c(
      "Hermitage Research Station",
      "Red Vale & Kingaroy Research Station",
      "Gatton",
      "Emerald Agricultural College",
      "Bongeen 1 & 2",
      "NGA - Premer",
      "NGA - Millmerran",
      "NGA - Marys Mount",
      "NGA - Goolhi",
      "Missen Flats",
      "Wellcamp"
   ),
   lat = c(
      -28.215 ,
      -26.58,
      -27.56,
      -23.54,
      -27.51666,
      -31.43449,
      -27.923674,
      -31.0142,
      -31.00246,
      -27.905313,
      -27.564277
   ),
   lon = c(
      152.1003,
      151.83,
      152.32,
      148.19,
      151.450,
      150.0052,
      151.242706,
      150.05018,
      149.82507,
      151.9772,
      151.867879
   )
)

write.csv(experiment_sites,
          "data/Mungbean_experiment_sites.csv",
          row.names = FALSE)

leaflet(experiment_sites) %>%
   addProviderTiles("Esri.WorldTopoMap") %>%
   setView(lat = -27.31,
           lng = 150.456,
           zoom = 5) %>%
   addMarkers(
      lng = ~ lon,
      lat = ~ lat,
      popup = ~ htmlEscape(location)
   )
```
